Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Community Detection and Parameter Estimation

### 2021-03-09 summary.Rmd
more cleanup

for some sparsity parameter $\lambda > 0$. The $c_i$ vectors are then collected 
into $C$ and $B$ as before.

Theorem 2 suggests that SSC is appropriate for community detection for the 
PABM. More precisely, Theorem 2 says that each community consists of a
$K$-dimensional subspace, and together the subspaces lie in $\mathbb{R}^{K^2}$. 
The natural approach then is to perform SSC on the ASE of $P$ or $A$.
\citet{noroozi2019estimation} instead applied SSC to $P$ and $A$ themselves.

Much of our work is built on top of work from 
\citet{rubindelanchy2017statistical}, in particular, the properties of the ASE 
of $A$ in relation to the ASE of $P$ built on $\{\lambda^{(kl)}\}_K$.

>>>>

for some sparsity parameter $\lambda > 0$. The $c_i$ vectors are then collected 
into $C$ and $B$ as before. The ability for this algorithm to identify the 
communities exactly is called the SSC detection property.

Theorem 2 suggests that SSC is appropriate for community detection for the 
PABM. More precisely, Theorem 2 says that each community consists of a
$K$-dimensional subspace, and together the subspaces lie in $\mathbb{R}^{K^2}$. 
The natural approach then is to perform SSC on the ASE of $P$ or $A$.
\citet{noroozi2019estimation} instead applied SSC to $P$ and $A$.

Using results from \citet{soltanolkotabi2012}, it can be easily shown that 
the SSC detection property holds for $XU$, which is an ASE of $P$. More 
specifically, if points lie exactly on mutually orthogonal subspaces, then the 
SSC detection property will hold with probability 1, and this is exactly the 
case for the PABM (Theorem 2). Much of our work is then built on \citet{ribindelanchy2017statistical}, who describe the convergence behavior of 
the ASE of $A$ to the ASE of $P$, and \citet{pmlr-v28-wang13}, who show the 
necessary conditions for the SSC detection property to hold in noisy cases 
where the points lie near subspaces.
